`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-17 inst/manuscript/manuscript.rmd
Minor clarifications in the 'Availability' section;

## Availability of data and materials {-}
The `R` package `flippant` provides all functionality as well as data presented
here along with extensive additional documentation and example code accessible
from within `R` in an integrated manner.

The package is available as an `R` source package in the version current at
acceptance for publication in the supplementary material and may be installed
from that file using ` install.packages(file.choose(), type = 'source')`.

@@

Thirdly the code base and development history is publicly accessible at \
`https://bitbucket.org/graumannlabtools/flippant`.

>>>>

## Availability of data and materials {-}
The `R` package `flippant` provides in an integrated manner and accessible
from within `R` all functionality as well as data presented here along with
extensive additional documentation and example code.

The package is available as an `R` source package in the version current at
acceptance for publication in the supplementary material and may be installed
from that file using `install.packages(file.choose(), type = 'source')`.

@@

Thirdly the code base and development history will, upon publication, be
publicly accessible at
[`https://bitbucket.org/graumannlabtools/flippant`](https://bitbucket.org/graumannlabtools/flippant).
